Optimizing the Robotics Closet

### 2018-11-16 paper.tex
formatting and spelling fix

\section{Improvements}
We noticed that the model packed together very many items while leaving four perfectly good shelves empty. Especially when considering that there are items we likely forgot to catalogue, as well as items that would get added later on, we may consider adding space remaining in shelves as a soft constraint. This could be done by either reducing the width of each shelf or by padding the items on all sides to imply that there must be room between each item. This would also have the added benefit of making items easier to take out, since it is illogicall to stuff some shelves to the last inch while leaving whole drawers to collect dust.

@@

\section{Acknowledgements}
We would like to thank:
- Dr. Sara Billey for providing us with guidance throughout the project,
- Hongyu Cao for supplying us with a paper that inspired a significant portion of our thoughts on the problem,
- UW Husky Robotics for providing the closet to undergo optimization,
- Nolan Donovan for working with us to understand and solve this problem.

\end{document}

>>>>

\section{Improvements}
We noticed that the model packed together very many items while leaving four
perfectly good shelves empty. Especially when considering that there are items
we likely forgot to catalogue, as well as items that would get added later on,
we may consider adding space remaining in shelves as a soft constraint. This
could be done by either reducing the width of each shelf or by padding the
items on all sides to imply that there must be room between each item. This
would also have the added benefit of making items easier to take out, since
it is illogical to stuff some shelves to the last inch while leaving whole
drawers to collect dust.

@@

\section{Acknowledgements}
We would like to thank:
\begin{itemize}
\item Dr. Sara Billey for providing us with guidance throughout the project,
\item Hongyu Cao for supplying us with a paper that inspired a significant portion of our thoughts on the problem,
\item UW Husky Robotics for providing the closet to undergo optimization,
\item Nolan Donovan for working with us to understand and solve this problem.
\end{itemize}
\end{document}
